Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-27 paper.tex
update

\section{Motivation and Problem Description}\label{problemDes}
\subsection{Motivation}\label{Motivation}

@@

\subsection{Problem Formulation}\label{Motivation}

@@

\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $q_{sim}(a, b)$ is a function that given a output-related concept $a$ of a service and a input-related concept $b$ of another service, it returns a concept similarity value between $a$ and $b$.

The $q_{sim}(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_1$, $N_2$ and $N$ measure the distances from an output-related concept $a$, an input-related concept $b$, a closest common ancestor of these two matched $a$ and $b$ to the top concept of an ontology $O$ respectively. $\lambda$ is set to 0 as we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper.

\begin{equation}
s_{p}{=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
\label{equation1}
\end{equation}

@@

\begin{equation}
\label{equation2}
sm(a, b) \stackrel{.}{=} ( type(a, b), \  q_{sim}(a, b) )
\end{equation}

\textbf{Weighted DAG Composition Model}. web service composition is considered to be a data workflow, where services are chained together by their inputs and outputs using the two models defined before. All these concepts are captured and tackled in a weighted DAG as $WG = (V, E)$ , where:

@@

Our comprehensive quality evaluation model is considered to be more general. Two semantic matchmaking types (Exact and Plugin) are considered for discovering desired web service in recent QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of matchmaking types and concept similarities in their approaches. Consequently, weights for $MT$ and $S$ are considered to be 0 in our proposed comprehensive evaluation model, it turns to be a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.
\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}

\begin{figure*}[h]
\centering
\fbox{\includegraphics[scale=.4]{overview.pdf}}
 \caption{Overview of POS-based approach to QoS-aware automated semantic web service composition.}
 \label{overview}
\end{figure*}

\subsection{PSO-based Approach to QoS-Aware Semantic Web Service Composition}\label{PSO_based_approach}

PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be easier to maintain the correctness of solutions compared to GP-based approaches that often require repairing or penalising the solutions \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both semantic matchmaking quality and QoS. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 5. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation with explicit support for the proposed quality model.

>>>>

\section{Motivation and Problem Description}\label{Motivation and Problem Description}
\subsection{Motivation}\label{Motivation}

@@

\subsection{Problem Formulation}\label{problemDes}

@@

\textbf{Definition 5.} Given $full match(a \Rightarrow b)$, $sim(a, b)$ is a function that given a output-related concept $a$ of a service and a input-related concept $b$ of another service, it returns a concept similarity value between $a$ and $b$.

The $sim(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_1$, $N_2$ and $N$ measure the distances from an output-related concept $a$, an input-related concept $b$, a closest common ancestor of these two matched $a$ and $b$ to the top concept of an ontology $O$ respectively. $\lambda$ is set to 0 as we do not measure the similarities of neighbourhood concepts, which is not the matching type considered in this paper.

\begin{equation}
sim(a, b){=} \frac{2N \cdot e^{-\lambda L/D} }{N_{1}+N_{2}}
\label{equation1}
\end{equation}

@@

\begin{equation}
\label{equation2}
sm(a, b) \stackrel{.}{=} ( type(a, b), \  sim(a, b) )
\end{equation}

\textbf{Weighted DAG composition model}. web service composition is considered to be a data workflow, where services are chained together by their inputs and outputs using the two models defined before. All these concepts are captured and tackled in a weighted DAG as $WG = (V, E)$ , where:

@@

Our comprehensive quality evaluation model is considered to be more general. Two semantic matchmaking types (Exact and Plugin) are considered for discovering desired web service in recent QoS-aware web service composition  \cite{ma2015hybrid,da2016particle,da2015graphevol}, but there are no measurements of matchmaking types and concept similarities in their approaches. Consequently, weights for $MT$ and $S$ are considered to be 0 in our proposed comprehensive evaluation model, it turns to be a widely used QoS evaluation model in \cite{ma2015hybrid,da2016particle,da2015graphevol}.

\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.4]{overview.pdf}}
 \caption{An overview of POS-based approach to comprehensive quality-aware automated semantic web service composition.}
 \label{overview}
\end{figure}

\subsection{An Overview to PSO-based Method}\label{PSO_based_approach}

PSO has shown its promising in solving combinatorial optimisation problems, which is considered to a easier way to maintain the correctness of solutions comparing to GP-based approaches that often require repairing or penalising the solutions \cite{da2016particle}. Therefore, we will employ a PSO-based approach to comprehensive quality-aware automated semantic web service composition. Fig. \ref{overview} shows an overview of our approach with five steps. Step 1: The composition process is triggered by a composition task defined in Subsection \ref{problemDes}. Step 2: This composition task is used to discover all task-related service candidates using a greedy search adopt from \cite{ma2015hybrid}. This algorithm keeps storing and adding outputs of the evocable services as available outputs, and these available outputs are used to discovery new services in service repository and updated themselves. This loop process does not stop until no service is satisfied by the available outputs. During the greedy search, an ontology-based cache is initialised, which stores the concept similarities of inputs and outputs of task-related candidate that demonstrated in SubSect. \ref{indexCache}. Step 3: Particle initialisation and mapping. In the initialisation, each particle's position size is determined by the size of task-related service candidates. Meanwhile, each service candidate are mapped to an index of a particle’s position vector (each vector have a weight value that falls between 0.0 and 1.0). After that, all the services are put in a queue and sorted according to their corresponding weight values in a descending order. This sorted queue is used to construct a weighted DAG. Step 4. Follows the standard PSO steps after step 3. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 5. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation with explicit support for the proposed quality model.
